Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-11-16 docs/papers/roofline_habakkuk/habakkuk.tex
Habakkuk paper - Begin to discuss multi-core performance

Shallow implementation of Sadourny~\cite{sadourny75}.

@@

Parse the (Fortran) source code.

>>>>

Shallow implementation of Sadourny~\cite{sadourny75}.
NEMOLite2D.

@@

Parse the (Fortran) source code.  Construct a Directed Acyclic Graph
to represent the source.  Use the properties of the DAG to
characterise the processed source.  At its simplest, this can just be
a count of FLOPs and memory (array) accesses.  Can then be extended to
allow for caching of consecutive array accesses as in stencil
operations in a direct-addressed model.

\subsubsection{Scheduling}

Obtaining a performance estimate by simply counting all of the FLOPs
that must be performed is equivalent to assuming that they are all
executed sequentially. However, a core a current CPU is likely to have
support for Instruction Level Parallelism.

\subsection{Single Instruction Multiple Data}

\subsection{Multi-core Performance}

So far we have considered only single-core performance. In reality,
any application seeking to achieve good performance will run in
parallel on multiple CPU cores.  If we restrict ourselves to running a
single process/thread per core then clearly that thread will have
exclusive use of that core's registers and execution units. Resources
shared between cores such as L2 cache or bandwidth to main memory will
however be shared by the executing threads.

\section{Results}

\subsection{Shallow}

\subsection{NEMOLite2D}

\subsection{Tracer Advection in NEMO}
